Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-10-07 README.Rmd
added an idea

- Final clean up and proof read of sections 4 and 5
- Prepare for submission (make sure to update date on cover letter)
- Upload the files for submission and submit

>>>>

- Add a sentence in the section on explanation scatterplots about removing the blindfold
- Final clean up and proof read of sections 4 and 5
- Prepare for submission (make sure to update date on cover letter)
- Upload the files for submission and submit
